---
title: "My PDF Report with R Markdown"
author:
- My Name
output: pdf_document
fontsize: 12pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, message=FALSE}
library("tximport")
library("readr")
library("tximportData")
dir <- system.file("extdata", package="tximportData")
```

## File Inputs

### Samples Sheet
```{r, echo=FALSE, message=FALSE}
samples2 <- read.table(file.path("/", "samples.txt"), head=TRUE)
samples2
```

### Salmon Quantification Inputs

```{r, echo=FALSE, message=FALSE}
files <- file.path("/", samples2$Sample, "quant.sf")
files
```


## Differential expression analysis

### DESeq2 Summary

The standard differential expression analysis steps are wrapped into a single function, DESeq. The estimation steps performed by this function are described below, in the manual page for ?DESeq and in the Methods section of the DESeq2 publication (Love, Huber, and Anders 2014).

#### DESeq2 Data Frame

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library("DESeq2")

tx2gene <- read_csv(file.path(dir, "tx2gene.gencode.v27.csv"))
txi <- tximport(files, type="salmon", tx2gene=tx2gene)

dds <- DESeqDataSetFromTximport(txi, colData = samples2, design = ~ Condition)
dds <- DESeq(dds)
res <- results(dds)
res
```

#### Summary Statistics

```{r, echo=FALSE, message=FALSE, warning=FALSE}
summary(res)
```

### DESeq2 Summary
